---
title: "Fitbit Interday"
author: "Benjamin W Nelson"
date: "1/2/2018"
output: html_document
---

#Steps to Download Interday Fitbit Data

##Install fitbitr package
```{r}
# install.packages("devtools")
library("devtools")
devtools::install_github("teramonagi/fitbitr")
devtools::install_github("teramonagi/fitbitr@issues-34")

```

##Resources:
This markdown was created by referencing these resoures.
Logon to https://dev.fitbit.com/login
https://github.com/teramonagi/fitbitr
https://dev.fitbit.com/build/reference/web-api/activity/


###Steps

####Load libraries
```{r}
library(fitbitr); library(ggplot2)
```

####Set the variables
```{r}
# As a global variable
FITBIT_KEY    <- "USE YOUR FITBIT KEY"
FITBIT_SECRET <- "USE YOUR FITBIT SECRET"
# If you want, Default: "http://localhost:1410/"
FITBIT_CALLBACK <- "http://localhost:1410/" 
url_base <- "https://api.fitbit.com/1/"
url_api  <- paste0(url_base, "user/-/")
```

####Get Token
```{r}
token <- fitbitr::oauth_token() #Old token
token <- fitbitr::oauth_token(language="en_US") #Set timezone
```

####Get Device Information
```{r}
get_devices(token)
```


#### Note on Variables:
-Base date: The range start date, in the format yyyy-MM-dd or today.
-End date: The end date of the range. You can put in "today" to pull data up to the most recent day of data
-Date: The end date of the period specified in the format yyyy-MM-dd or today.
-Period: The range for which data will be returned. Options are 1d, 7d, 30d, 1w, 1m, 3m, 6m, 1y


##ACTIVITY
```{r}
url_activity <- paste0(url_api, "activities/")
```

####Get Heart Rate
```{r}
hr <- get_activity_time_series(token, "restingHeartRate", base_date="2016-02-10", end_date="today")
hr
colnames(hr) <- c("date","resting.heart.rate") #This renames the columns
hr
```

####Get Steps
```{r}
steps <- get_activity_time_series(token, "steps", base_date="2016-02-10", end_date="today")
steps
colnames(steps) <- c("date","steps") #This renames the columns
steps
```

####Get Distance
```{r}
distance <- get_activity_time_series(token, "distance", base_date="2016-02-10", end_date="today")
distance
colnames(distance) <- c("date","distance") #This renames the columns
distance
```

####Get Floors
```{r}
floors <- get_activity_time_series(token, "floors", base_date="2016-02-10", end_date="today")
floors
colnames(floors) <- c("date","floors") #This renames the columns
floors
```

```{r}
get_activity_time_series <- function(token, resource_path, date="", period="", base_date="2016-02-10", end_date="today", simplify=TRUE)
get_activity_time_series
```


####Minutes Sedentary
```{r}
min.sedentary <- get_activity_time_series(token, "minutesSedentary", base_date="2016-02-10", end_date="today")
min.sedentary
colnames(min.sedentary) <- c("date","minutes.sedentary") #This renames the columns
min.sedentary
```

####Minutes Lightly Active
```{r}
min.lightly.active <- get_activity_time_series(token, "minutesLightlyActive", base_date="2016-02-10", end_date="today")
min.lightly.active
colnames(min.lightly.active) <- c("date","minutes.lightly.active") #This renames the columns
min.lightly.active
```

####Minutes Fairly Active
```{r}
min.fairly.active <- get_activity_time_series(token, "minutesFairlyActive", base_date="2016-02-10", end_date="today")
min.fairly.active
colnames(min.fairly.active) <- c("date","minutes.fairly.active") #This renames the columns
min.fairly.active
```

####Minutes Very Active
```{r}
min.very.active <- get_activity_time_series(token, "minutesVeryActive", base_date="2016-02-10", end_date="today")
min.very.active
colnames(min.very.active) <- c("date","minutes.very.active") #This renames the columns
min.very.active
```

####Get Active Calories
```{r}
calories <- get_activity_time_series(token, "calories", base_date="2016-02-10", end_date="today")
calories
colnames(calories) <- c("date","calories.burned") #This renames the columns
calories
```


##SLEEP
```{r}
url_sleep <- paste0(url_api, "sleep/")
```

####Get Sleep- Time in Bed
```{r}
timeinbed <- get_sleep_time_series(token, "timeInBed", base_date="2016-02-10", end_date="today")
timeinbed
colnames(timeinbed) <- c("date","time.in.bed") #This renames the columns
timeinbed
```

####Get Sleep- Minutes Asleep
```{r}
sleep.minutes.asleep <- get_sleep_time_series(token, "minutesAsleep", base_date="2016-02-10", end_date="today")
sleep.minutes.asleep
colnames(sleep.minutes.asleep) <- c("date","sleep.duration") #This renames the columns
sleep.minutes.asleep
#This is the same as Sleep Duration when you download from fitbit
```

####Get Sleep- Minutes Awake
```{r}
sleep.minutes.awake <- get_sleep_time_series(token, "minutesAwake", base_date="2016-02-10", end_date="today")
sleep.minutes.awake
colnames(sleep.minutes.awake) <- c("date","minutes.awake") #This renames the columns
sleep.minutes.awake
```

####Get Sleep- Efficency
```{r}
sleep.efficiency <- get_sleep_time_series(token, "efficiency", base_date="2016-02-10", end_date="today")
sleep.efficiency
colnames(sleep.efficiency) <- c("date","sleep.efficiency") #This renames the columns
sleep.efficiency
```

####Get Sleep- Minutes to Fall Asleep
```{r}
time.to.sleep <- get_sleep_time_series(token, "minutesToFallAsleep", base_date="2016-02-10", end_date="today")
time.to.sleep
colnames(time.to.sleep) <- c("date","sleep.onset.latency") #This renames the columns
time.to.sleep
#This is usually 0 for auto logs
```

####Get Sleep- Number of Awakenings
```{r}
sleep.number.awakenings <- get_sleep_time_series(token, "awakeningsCount", base_date="2016-02-10", end_date="today")
sleep.number.awakenings
colnames(sleep.number.awakenings) <- c("date","number.of.awakenings") #This renames the columns
sleep.number.awakenings
#This is different from what is downloaded from fitbit
```

##BODY

####Get Body Composition- Weight
```{r}
weight <- get_body_time_series(token, "weight", base_date="2016-02-10", end_date="today")
weight
colnames(weight) <- c("date","weight") #This renames the columns
weight
```

####Get Body Composition- BMI
```{r}
bmi <- get_body_time_series(token, "bmi", base_date="2016-02-10", end_date="today")
bmi
colnames(bmi) <- c("date","bmi") #This renames the columns
bmi
```

####Get Body Composition- Fat
```{r}
fat <- get_body_time_series(token, "fat", base_date="2016-02-10", end_date="today")
fat
colnames(fat) <- c("date","body.fat.percentage") #This renames the columns
fat
```

####Get Body Composition- Lean
```{r}

#Need to finish figuring this out
```

####Merge Datasets
```{r}
library(tidyverse)
fitbit.interday <- plyr::join_all(list(hr, steps, distance, floors, calories, timeinbed, time.to.sleep, sleep.minutes.asleep, sleep.minutes.awake, sleep.number.awakenings, sleep.efficiency, weight, bmi, fat))
```


