---
title: "Fitbit Intraday Data"
author: "Benjamin W Nelson"
date: "1/2/2018"
output: html_document
---

##Resources:
This markdown was created by referencing these resoures.
Logon to https://dev.fitbit.com/login
https://github.com/teramonagi/fitbitr
https://dev.fitbit.com/build/reference/web-api/activity/

```{r}
# install.packages("devtools")
devtools::install_github("teramonagi/fitbitr")
```


Logon to https://dev.fitbit.com/login

Set the variables
```{r}
# As a global variable
FITBIT_KEY    <- "USE YOUR FITBIT KEY"
FITBIT_SECRET <- "USE YOUR FITBIT SECRET"
FITBIT_CALLBACK <- "http://localhost:1410/" 
```

Load libraries
```{r}
library(fitbitr); library(ggplot2)
```

Get Token
```{r}
token <- fitbitr::oauth_token()
```

Get Device Information
```{r}
get_devices(token)
```


Variables:
-Base date: The range start date, in the format yyyy-MM-dd or today.
-End date: The end date of the range
-Date: The end date of the period specified in the format yyyy-MM-dd or today.
-Period: The range for which data will be returned. Options are 1d, 7d, 30d, 1w, 1m, 3m, 6m, 1y

Set The Date you Want
```{r}
date <- "2018-01-01"
```

Steps
```{r}
steps <- get_activity_intraday_time_series(token, "steps", date, detail_level="15min")
steps
```

Graph Steps
```{r}
ggplot(steps, aes(x=time, y=value)) + geom_line()
```

Get Heart Rate
```{r}
hr <- get_heart_rate_intraday_time_series(token, date=date, detail_level="15min")
hr
```

Graph Heart Rate
```{r}
ggplot(hr, aes(x=time, y=value)) + geom_line()
```



